Testing Charts: viewer's perceptual accuracy in surveys

### 2023-06-16 SDSS-2023/testing-charts-accuracy.qmd
set up for edits

---
title: "Testing Charts: viewer's perceptual accuracy in surveys"
bibliography: references.bib
abstract: " "
keywords: 'list, keywords, here, 3-6, are, fine'
format: 
  pdf:
    include-in-header:
     # - edits.tex
      - authors.tex
      # - refs.tex
    keep-tex: true
    # template: template.tex
documentclass: jds
---

@@

# Introduction

>>>>

---
title: "Testing Charts: viewer's perceptual accuracy in surveys"
bibliography: references.bib
abstract: " "
keywords: 'list, keywords, here, 3-6, are, fine'
format: 
  pdf:
    include-in-header:
      - edits.tex
      - authors.tex
      # - refs.tex
    keep-tex: true
    # template: template.tex
documentclass: jds
---

@@

\hh{This is Heike's color for making changes}
# Introduction
